Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex
removed TODO
style changes

\section*{TODO}

\begin{itemize}
	\item changer CDF
	\item Expliquer simulation plus en d\'etail (GLPK)
	\item Donner un algo pour CRP
	\item fix bibliography
\end{itemize}

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if there is one), because for a given set of $a_i$ values they are
		very similar to an instance of the Chinese Remainder Problem (CRP), which is
		easily solved using Gauss's CRP solving method for non-coprime moduli
		\cite{gauss1965disquisitiones}.

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A better method for finding the
		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
		shown in Algorithm~\ref{alg:multiACRP}.

@@

		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
		speedup is achieved by first computing all possible terms for each task
		then creating all possible DIT values by summing the terms in all possible
		ways. The number of results is still exponential in the number of tasks, but
		the only operation that is repeated exponentially many times is now a sum.
		This allows us to profit from the high chance of having DITs when the CDF
		factor is close to one, but with only a slight increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.eps}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value
	of the CDF has a greater influence on this ratio than the system's total
	utilization, but less so when the CDF is lower. It is also important to note
	that even though a 0.95 ratio may not seem much, the synchronous C-spaces of
	the systems contain many dominated WCET vectors, and only those that are
	in the border (i.e. non-dominated) actually matter to the designer of the system.
	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
	solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.

>>>>

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values they are
		very similar to an instance of the Chinese Remainder Problem (CRP), which is
		easily solved using Gauss's CRP solving method for non-coprime moduli
		\cite{gauss1965disquisitiones}.

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A better method for finding the
		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
		shown in Algorithm~\ref{alg:multiACRP} (note that $x^{-1} \; (mod \; y)$
		means the modular inverse of $x$ in the naturals modulo $y$).

@@

		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
		speedup is achieved by first computing all possible terms for each task
		then creating all possible DIT values by summing the terms in all possible
		ways. The number of results is still exponential in the number of tasks, but
		the only operation that is repeated exponentially many times is now a sum.
		This allows us to profit from a high chance of having DITs when the deadlines
		are close to the WCETs (and far from the periods), but with only a slight
		increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). As calculating those
	sizes is rather long, the number of systems used to obtain average
	results was rather low (1000), which is the likely cause of the spikes in the
	data. Note that the value of the CDF has a greater influence on this ratio than
	the system's total utilization, but less so when the CDF is lower. It is also
	important to note that even though a 0.95 ratio may not seem much, the
	synchronous C-spaces of the systems contain many dominated WCET vectors, and
	only those that are in the border (i.e. non-dominated) actually matter to the
	designer of the system. Using the asynchronous C-space instead will relax some
	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.
